Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-07-15 Report/introduction.tex
updated intro

We consider the problem of resource allocation for a multi-cell \ac{MU-MIMO} transmission over an \ac{OFDM} system with the objective of minimizing the total number of backlogged packets of all users at a given instant. The available space and frequency resources in the considered system are shared among the users by \ac{BS} cooperation in order to minimize the number of packets waiting for transmission from each \ac{BS} to the respective users. In this paper, beamforming technique is utilized at \acp{BS} and linear single-user detection is employed at each receiver, i.e., the inter-user interference is treated as background noise. The queue minimizing network optimization objective is used to design beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets. To achieve the best performance, we propose a joint resource allocation scheme over the space and frequency dimensions among the coordinating \acp{BS} to minimize the time that the packets stay in queues prior to transmission, and, hence, to avoid packet drops as an indirect objective.

Many existing beamformer designs for similar system models addresses the problem of \ac{WSRM} objective. By adjusting the weights properly, we can use the \ac{WSRM} schemes to achieve other performance measures. For example, if the weight of each user is set to be inversely proportional to his/her data rate, a \ac{WSRM} scheme can maintain fairness among users. Similarly, the \ac{WSRM} schemes can be used to solve the design problem considered in this paper. Specifically, to find a rate vector that minimizes the number of queued packets, we should assign weights based on the current queue size of users. More explicitly, the queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or a function depending on it \cite{neely2010stochastic}, where the \ac{Q-WSRM} scheme is the outcome of minimizing the Lyapunov drift between the current and the future queue states.

The topic of \ac{MIMO} \ac{BC} precoder design has been studied extensively with different performance criteria in the literature. For the problem of \ac{WSRM} utility, due to the nonconvex nature of the linear \ac{MIMO} \ac{BC} precoder design, \cite{christensen2008weighted,wmmse_shi} addressed the problem using a reformulation via \ac{MMSE}, casting the problem as a convex one for  fixed receivers. In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders. Then the problem is solved using an alternating optimization method, i.e., finding a set of variables while the remaining others are fixed. The \ac{WSRM} problem using an alternative \ac{MMSE} reformulation along with the additional rate constraints is considered in \cite{kaleva2013primal}. A fast converging algorithm for the \ac{WSRM} problem is proposed in \cite{tran2012fast} using a surrogate for a convex program at each iteration.

Earlier work on the queue minimization problem was addressed in the survey paper \cite{berry2004cross} and in particular \cite{qps_cioffi}, where the problem of optimal power allocation is considered to minimize the number of backlogged packets via \acl{GP} formulation. Since the problem considered in \cite{qps_cioffi} assumes multi-user \ac{OFDM} model without multi-antenna support, the queue minimizing scheduling reduces to the problem of optimal power allocation.

In this paper, we consider the problem of designing the precoders for a \ac{MU-MIMO} \ac{OFDM} scenario jointly across space-frequency dimension to minimize the number of queued packets associated with the users. We compare the performance of the proposed \ac{QM} \ac{JSFRA} scheme over the \ac{Q-WSRM} scheme performed over each sub-channel, where the weights are updated after each sub-channel with the unserved packets. We show that the \ac{JSFRA} scheme provides better performance over the sub-channel wise resource allocation technique like \ac{Q-WSRM} scheme.

>>>>

The last mile wireless connectivity poses significant bottleneck in the overall data traffic in the interconnected networks. The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which is proportional to the battery drain. In order to over come the receiver complexity, \ac{OFDM} based transmissions are introduced for the wideband transmissions. To improve the data rate, multiple antennas are installed at the \ac{BS} and at the user terminals to avail the additional freedom in the form of spatial dimension. The inclusion of \ac{MIMO} technique in the wireless network provides increased data rate or lower outage for the same transmission power and the channel use.

In a network with multiple \acp{BS} serving multiple users (\acs{MU}), the main driving factor for the transmission are the packets waiting at each \ac{BS} corresponding to the different users present in the network. These available packets are transmitted over the shared wireless resources in an efficient manner with the various system constraints. In this work, we consider the user allocation over the space-frequency resources provided by the \ac{MU-MIMO} \ac{OFDM} framework in the downlink broadcast transmission to reduce the number of queued packets corresponding to the users at the \acp{BS}. Since the space-frequency resources are shared by multiple users associated with different \acp{BS}, the problem can be considered as a resource allocation to minimize the number of backlogged packets at the \acp{BS}.

In general, the resource allocation problems are solved by assigning a binary variable to each user indicating the presence or the absence on a particular resource. In contrast to that, we use the transmit beamformers, which are the complex vectors, as a decision variable in determining the presence or the absence of a user on a particular resource. The purpose of using the transmit beamformers for the scheduling is two fold. Firstly, it determines the transmission rate on a certain resource and secondly, by making the transmit beamformer to be a zero vector, the corresponding user will not be scheduled on a certain resource. The queue minimizing network optimization objective is used to design beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets. To achieve the best performance, we propose a joint resource allocation scheme over the space and frequency dimensions among the coordinating \acp{BS} to minimize the time that the packets stay in queues prior to transmission, and, hence, to avoid packet drops as an indirect objective.

The queue minimizing precoder designs are nothing but the \ac{WSRM} problem with the additional rate constraint determined by the number of backlogged packets for each user in the system. The topic of \ac{MIMO} \ac{BC} precoder design has been studied extensively with different performance criteria in the literature. Due to the nonconvex nature of the linear \ac{MIMO} \ac{BC} precoder design problem, it is solved by the sequence of approximated convex problems. In \cite{sin_algorithm}, the \ac{MIMO} rate expression is linearized around a fixed point in order to solve the \ac{DC} problem as a concave maximization problem in an iterative manner. Similar approach of solving the \ac{WSRM} problem via arithmetic-geometric inequality is proposed in \cite{tran2012fast}, providing better convergence rate compared to the former.

The relation between the achievable capacity and the \ac{MSE} for the received symbol by using the fixed \ac{MMSE} receivers as shown in \cite{viswanath1999optimal,mse_duality} are also used to solve the \ac{WSRM} objective. In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MMSE}, casting the problem as a convex one for fixed \ac{MMSE} receivers. In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and decoders. Then the problem is solved using an alternating optimization method, i.e., finding a set of variables while the remaining others are fixed. Additional rate constraints based on the \ac{QoS} requirements are included in the \ac{WSRM} objective are solved via \ac{MSE} reformulation in \cite{kaleva2013primal}.

The problem of precoder design for the \ac{MIMO} \ac{BC} system are solved either by using the centralized controller or at each \ac{BS} independently by exchanging limited information via backhaul. The distributed approaches are performed using the primal or by the dual decomposition. In primal decomposition, the coupling interference variables are fixed for each \ac{BS} wise subproblems and solved for the optimal precoders. The fixed interference are then updated by using the subgradients as discussed in \cite{pennanen2011decentralized}. The dual approach controls the distributed subproblems by fixing the interference price for each \ac{BS} as detailed in \cite{tolli2011decentralized}.

By adjusting the weights properly, we can use the \ac{WSRM} schemes to achieve other performance measures. For example, if the weight of each user is set to be inversely proportional to his/her data rate, a \ac{WSRM} scheme can maintain fairness among users. Similarly, the \ac{WSRM} schemes can be used to solve the design problem considered in this paper. Specifically, to find a rate vector that minimizes the number of queued packets, we should assign weights based on the current queue size of users. The queue states can be incorporated to traditional weighted sum rate objective $\sum_k w_k R_k$ by replacing the weight $w_k$ with the corresponding queue state $Q_k$ or a function depending on it \cite{tassiulas,neely2010stochastic}, which is the outcome of minimizing the Lyapunov drift between the current and the future queue states. Similar algorithms are discussed in the networking literature as the backpreassure algorithm, where the differential queues between the source and the destination nodes are used as the weights scaling the transmission rate \cite{georgiadis2006resource}.

Earlier work on the queue minimization problem was addressed in the survey paper \cite{berry2004cross} and in particular \cite{qps_cioffi}, where the problem of optimal power allocation is considered to minimize the number of backlogged packets via \acl{GP} formulation. Since the problem considered in \cite{qps_cioffi} assumes multi-user \ac{OFDM} model without multi-antenna support, the queue minimizing scheduling reduces to the problem of optimal power allocation. In the context of the wireless networks, the backpreassure algorithm has been extended by formulating the wireless transmission rate as a \ac{MIMO} \ac{BC} optimization problem by using the corresponding user queues as the weight for the associated rate \cite{weeraddana2011resource}.

In the traditional \ac{WSRM} formulation, the precoders are designed for the sub-channels independently due to the interference-free \ac{OFDM} transmission. In this work, since the objective is to identify the transmission rates for all the users across the space-frequency resources, the precoders are to be designed jointly across the space-frequency dimension. In order minimize the number of queued packets at the \acp{BS}, the precoders are designed by the proposed \ac{JSFRA} formulation with two different approaches in a centralized manner. We also propose the distributed approaches for the centralized problem for designing the precoders independently across the \acp{BS} with the limited information exchange.

The outline of this paper is as follows. In Section \ref{sec-2-3.2}, we propose the system model and the problem formulation for the current queue minimizing precoder design. Existing and the proposed precoder designs for the queue minimizing objective is discussed elaborately in Section \ref{sec-3}. The distributed solutions are outlined in Section \ref{sec-4} followed by the simulation results for both centralized and the distributed algorithms are provided in Section \ref{sec-5}. Conclusions are drawn in Section \ref{sec-6}.

### 2014-07-15 Report/mse_formulation.tex
updated intro

In this section, we present an alternative formulation for the \acl{QM} \ac{JSFRA} scheme by using the \ac{MSE} equivalence with the capacity as in \cite{christensen2008weighted,wmmse_shi} for the \ac{WSRM} problem. The current formulation uses the well known relation between the capacity and the \ac{MSE} given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon} \right )} \cite{viswanath1999optimal,mse_duality}, where \me{\epsilon = {1} / {(1 + \gamma)}} is the \ac{MSE} for decoding the transmitted symbols using the \ac{MMSE} receivers and \me{C} is the maximum achievable capacity for a given \ac{SINR} of \me{\gamma}. Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denotes the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent. Now, using the \ac{MSE} relation, \eqref{eqn-6} is written as
\begin{IEEEeqnarray}{LL}\label{eqn-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}), \IEEEyessubnumber \label{eqn-mse-1.2} \\
 & \quad \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
& \quad \text{and} \; \eqref{eqn-4.3},  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
where \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}} and \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the the \ac{MSE} relation.

>>>>

In this section, we present an alternative approach for solving the \acl{QM} \ac{JSFRA} problem by using the \ac{MSE} equivalence with the the achievable capacity presented in \cite{viswanath1999optimal,mse_duality}. It is given by \me{C(\gamma) = \log_2 \left ( {1}/{\epsilon(\gamma)} \right )}, where \me{\epsilon(\gamma) = {1} / {(1 + \gamma)}} is the \ac{MSE} for decoding the transmitted symbol at the reciever employing the \ac{MMSE} equalizer and \me{C(\gamma)} is the achievable capacity for the \ac{SINR} of \me{\gamma}. Using this equivalence, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} objective to obtain the precoders for the \ac{MU-MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi}. In the current approach, we use this relation between the \ac{MSE} and the achievable capacity to solve the \ac{JSFRA} problem by employing \ac{MMSE} receivers.

Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denotes the queue deviation corresponding to the user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent. Now, using the \ac{MSE} relation, \eqref{eqn-6} is written as
\begin{IEEEeqnarray}{LL}\label{eqn-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}), \IEEEyessubnumber \label{eqn-mse-1.2} \\
 & \quad \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,i,n} \mvec{m}{j,i,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{eqn-mse-1.3} \\
& \quad \text{and} \; \eqref{eqn-4.3},  \IEEEyessubnumber \label{eqn-mse-1.4}
\end{IEEEeqnarray}
where \eqref{eqn-mse-1.3} bounds the \ac{MSE} by \me{\epsilon_{l,k,n}} and \eqref{eqn-mse-1.2} relaxes the transmitted rate \me{{t}_{l,k,n}} using the the \ac{MSE} relation.

### 2014-07-15 Report/simulation_distributed.tex
Signed-off-by: Ganesh <gvenkatr@ee.oulu.fi>
updated intro

In this section, we discuss the simulation performances of the algorithms briefed in Section \ref{sec-3} and \ref{sec-4}. The comparison studies are made using the queue deviation and sum rate convergence of the algorithms discussed so far using different system models. The distributed algorithms for the \ac{JSFRA} scheme and the equivalent \ac{MSE} representation are compared using the excess backlogged packets present after the current iteration instant.

Fig. \ref{fig-d-1} demonstrates the performance of the distributed algorithms in an \ac{OFDM} framework modeled with \me{N = 5} sub-channels with \me{N_B = 2} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas. Each \ac{BS} serves \me{|\mc{U}_b| = 4, \forall b \in \{1,2\}} users in a coordinated manner so as to minimize the interference caused to the neighboring \ac{BS} users. Fig. \ref{fig-d-1.1} shows the total number of backlogged packets at the end of each iteration and Fig. \ref{fig-d-1.2} plots the total rate achieved by various algorithms at each iteration. As discussed earlier in the distributed section, the rate of convergence of any distributed algorithm depends on the proper choice of a step size. In particular, the primal decomposition method is more susceptible to the choice of the step size compared to the \ac{ADMM} approach. Since the primal decomposition iterates at each instant by fixing the interference thresholds, it may lead to infeasible solutions if the initial interference values are not feasible and also with the updated interference value as in \eqref{primal-sg-update}.

Fig. \ref{fig-d-1} also compares the performance of the iterative algorithm for \ac{JSFRA} scheme via \ac{MSE} reformulation using the \ac{KKT} conditions discussed in Section \ref{sec-4.3}. The performance is inferior compared to the other algorithms due to the violation in the assumptions made in the algorithm design \textit{i.e}, \me{Q_k \gg t_k}. Since in this case, we are comparing the \me{q = 1} case, the queue condition \me{Q_k \gg t_k} needs to be satisfied in order to remove the absolute operator from the expression in \eqref{eqn-9.1a} to form \eqref{kkt-mse-1.1}. The total number of backlogged packets after the each iteration reduces monotonically in all cases and converges to the points closer to the centralized solution \me{\chi = 33} bits. As seen in Fig. \ref{fig-d-1}, the \ac{ADMM} approach provides better convergence compared to the primal approach in the initial phase due to the quadratic penalty term included in the objective, which gets pronounced initially due to the large deviation between the assumed and the actual interference across the coordinating \acp{BS}.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{NewFigures/distribute_queue-1}
\caption{Queue deviation}
\label{fig-d-1.1}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{NewFigures/distribute_sum_rate-1}
\caption{Sum rate performance}
\label{fig-d-1.2}
\end{subfigure}
\caption[short]{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace} model}
\label{fig-d-1}
\end{figure*}

@@

The performance of the joint \ac{Q-WSRM} scheme discussed in the Section \ref{sec-3.1} performs slightly worse than (\me{\approx \, 2} bits) the \ac{JSFRA} scheme in reducing the number of queued packets, even though the performance were similar in Table \ref{tbl-1}. As stated earlier, the joint \ac{Q-WSRM} scheme and the \ac{JSFRA} scheme with the exponent \me{q = 1} performs the same when the number of queued packets are identical for all the users. In this case, the joint \ac{Q-WSRM} becomes the sum rate maximization problem which is equivalent to the greedy \me{q=1} \ac{JSFRA} scheme. In the current scenario, since the number of queued packets are different for the users, the performance of the \ac{JSFRA} scheme is better due to its greedy resource allocation. It can be seen from Fig. \ref{fig-d-2}, that the \ac{KKT} based approach provides inferior result in the queue minimization perspective as compared with the sum rate plot. The performance degradation is due to the unconstrained rate increase for the users beyond their actual number of queued packets available to transmit. Since the objective uses the \me{\ell_1} minimization, the \ac{KKT} solution is not optimal unless the queues are far greater than the transmission rate available for each user. The number of queued packets are initialized in a way to analyze the effect of the unconstrained behavior in the \ac{KKT} scheme.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{NewFigures/distributed_queue_plot_1}
\caption{Queue deviation}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{NewFigures/distributed_sum_rate_plot_1}
\caption{Sum rate performance}
\end{subfigure}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,3,12,2 \rbrace} model}
\label{fig-d-2}
\end{figure*}

>>>>

In this section, we discuss the simulation performances of the algorithms briefed in Section \ref{sec-3} and \ref{sec-4}. The comparison studies are made using the queue deviation and sum rate convergence using various system models. The distributed algorithms for the \ac{JSFRA} scheme and the equivalent \ac{MSE} representation are compared using the excess backlogged packets present after each \ac{SCA} update.

Fig. \ref{fig-d-1} demonstrates the performance of the distributed algorithms in an \ac{OFDM} framework modeled with \me{N = 3} sub-channels with \me{N_B = 2} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas. Each \ac{BS} serves \me{|\mc{U}_b| = 4, \forall b \in \{1,2\}} users in a coordinated manner to reduce the number of backlogged packets at each \ac{BS}. Fig. \ref{fig-d-1.1} shows the total number of backlogged packets  and Fig. \ref{fig-d-1.2} plots the total rate achieved by different algorithms after each \ac{SCA} update. As pointed out earlier, the distributed algorithms are very much dependent on the choice of the step size used to update the subgradients. In particular, the primal decomposition is more susceptible to the step size as compared to the \ac{ADMM} approach, since interference values are fixed for each primal exchange, it may lead to infeasible solutions if the initial or any intermediate update on the interference determined by \eqref{primal-sg-update} are not in the valid range.

Fig. \ref{fig-d-1} also compares the performance of the iterative algorithm for \ac{JSFRA} scheme via \ac{MSE} reformulation using the \ac{KKT} conditions discussed in Section \ref{sec-4.3}. The performance is inferior compared to the other algorithms due to the violation in the assumptions made in the algorithm design \textit{i.e}, \me{Q_k \gg t_k}. Since in this case, we are comparing the \me{q = 1} case, the queue condition \me{Q_k \gg t_k} needs to be satisfied in order to remove the absolute operator from the expression in \eqref{eqn-9.1a} to form \eqref{kkt-mse-1.1}. The total number of backlogged packets after the each iteration reduces monotonically in all cases and converges to the points closer to the centralized solution \me{\chi = 33} bits. As seen in Fig. \ref{fig-d-1}, the \ac{ADMM} approach provides better convergence compared to the primal approach in the initial phase due to the quadratic penalty term included in the objective, which gets pronounced initially due to the large deviation between the assumed and the actual interference across the coordinating \acp{BS}.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{fig-3}
\caption{Queue deviation}
\label{fig-d-1.1}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{fig-4}
\caption{Sum rate performance}
\label{fig-d-1.2}
\end{subfigure}
\caption[short]{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} model}
\label{fig-d-1}
\end{figure*}

@@

The performance of the joint \ac{Q-WSRM} scheme discussed in the Section \ref{sec-3.1} performs slightly worse than (\me{\approx \, 2} bits) the \ac{JSFRA} scheme in reducing the number of queued packets, even though the performance were similar in Table \ref{tbl-1}. As stated earlier, the joint \ac{Q-WSRM} scheme and the \ac{JSFRA} scheme with the exponent \me{q = 1} performs the same when the number of queued packets are identical for all the users. In this case, the joint \ac{Q-WSRM} becomes the sum rate maximization problem which is equivalent to the greedy \me{q=1} \ac{JSFRA} scheme. In the current scenario, since the number of queued packets are different for the users, the performance of the \ac{JSFRA} scheme is better due to its greedy resource allocation. It can be seen from Fig. \ref{fig-d-2}, that the \ac{KKT} based approach provides inferior result in the queue minimization perspective as compared with the sum rate plot. The performance degradation is due to the unconstrained rate increase for the users beyond their actual number of queued packets available to transmit. Since the objective uses the \me{\ell_1} minimization, the \ac{KKT} solution is not optimal unless the queues are far greater than the transmission rate available for each user. The number of queued packets are initialized in a way to analyze the effect of the unconstrained behavior in the \ac{KKT} scheme.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{NewFigures/distributed_queue_plot_1}
\caption{Queue deviation}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{NewFigures/distributed_sum_rate_plot_1}
\caption{Sum rate performance}
\end{subfigure}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 2,3,9,2 \rbrace} model}
\label{fig-d-2}
\end{figure*}
